quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-20 paper-quollr.Rmd
Started working on Figure 6 title update

      # Caption
      tags$p(
        tags$strong("Figure 6:"), 
        " Comparison of the published model with the best selected model."
      )
    )
  )
)

>>>>

      # Caption
      tags$p(
        tags$strong("Figure 6:"), 
        "Compare the published $2-\\text{D}$ layout (Figure \\@ref(fig:limb-rmse) b) and the $2-\\text{D}$ layout selected (Figure \\@ref(fig:limb-rmse) f) by RMSE plot (Figure \\@ref(fig:limb-rmse)) from the tSNE, UMAP, PHATE, TriMAP, and PaCMAP with different (hyper)parameters. The Limb muscle data ($n =  1067$) has seven close different shaped clusters in $10\\text{-}D$."
      )
    )
  )
)
